%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Axonius Inc.} % Organization
    {Remote} % Location
    {May 2022 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Was the first member of the Portuguese tech cluster.}
        \item {Focused on growing tech knowledge for the new team.}
        \item {Supported and created multiple adapters that allowed us to show security concerns and
connections to the clients.}
        \item {\textbf{Tech Stack:} Python, Mongo, AWS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Research and Development Engineer} % Job title
    {Farfetch LC.} % Organization
    {Remote} % Location
    {2021 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {The first member of the Research and Development team focused on investing in new tech solutions in areas like:}
        \begin{itemize}
         \item Virtual reality
         \item Distributed computing (Blockchain and IPFS)
        \end{itemize}
        \item {Was a node operator of the Diem Consortium Blockchain (formerly called Libra by Facebook/Meta) alongside elements from Spotify, Uber, Shopify, and many.}
        \item {Created a POC for virtual reality that allows clients to see 3D digital assets on the phone apps}
        \item {Used Nvidia Geforce Now API and Google Stadia}
        \item {Started the Product Verity initiative project}
        \begin{itemize}
         \item Uses tags with random patterns to identify real luxury items. "Is this Gucci jacket really authentic? Let me take a photo of the unique pattern and check"
         \item Then provides the real owner a unique digital certificate (an NFT on the blockchain) that identifies and validates the product.
         \item The owner that way can resell or present their personal collection on a safe manner on the market
        \end{itemize}
        \item {\textbf{Tech Stack:} Dotnet, Typescript, Solidity (Ethereum blockchain programming language), Rust, Kafka, MSSQL, Cassandra, Docker, ArgoCD, Azure, OpenAPi, and Kubernetes.}
      \end{cvitems}
    }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Farfetch LC.} % Organization
    {Porto, Portugal} % Location
    {2020 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architectural role in the arch cluster at Farfetch}
        \item {Created and managed multiple company-critical projects like:}
        \begin{itemize}
         \item The Globalization project that allows micro-services to handle multi-country requirements (location, time-zones, best delivery paths, and other metrics)
         \item The Communication Hub, a highway for internal communications of all the micro-services based on Kafka, used in internal communications and external contact to clients via SMS/Email/Webhooks/Integration's and others
        \end{itemize}
        \item Beta team for the new deployment system using Elm Chart and ArgoCd
        \item {\textbf{Tech Stack:} Dotnet, Python, Kafka, MSSQL, Cassandra, Docker, Azure, ArgoCD, OpenAPi and Kubernetes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Critical Manufacturing} % Organization
    {Maia, Portugal} % Location
    {2018 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Core team developer for the manufacturing execution system (MES) that manages complex production pipelines}
        \item {The product development team creates and manages the main framework for
developing a highly flexible MES that adapts to different clients like:}
        \begin{itemize}
         \item Renault, BMW, IKEA, Braun, Philips, Johnson \& Johnson, and many others 
        \end{itemize}
        \item Worked on the Migration Task Force responsible for migrating the legacy system, for a more robust and modern alternative
        \item {\textbf{Tech Stack:} Dotnet, Angular, Typescript, MSSQL, Docker, Docker Swarm (moved to K8s) and Kubernetes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {E-Goi} % Organization
    {Matosinhos, Portugal} % Location
    {2017 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and maintained of the E-Goi Marketing system.}
        \item {Provided mechanisms to allow communication using Push notification, SMS, Email, voice marketing, and many others.}
        \item {\textbf{Tech Stack:} Laravel, Postgres, Redis, Vue, Linux.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Software Engineer} % Job title
    {E-Goi} % Organization
    {Matosinhos, Portugal} % Location
    {2016 - 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created the Sync2E-goi project that: Allows clients to integrate platforms to the E-goi marketing.}
        \item {Allowed Costumers to leave competitors like Mailchimp and migrate to the company Uses external systems like Zappier to improve the current E-Goi platform with minimal configuration}
        \item {\textbf{Tech Stack:} Laravel, Postgres, Redis, Vue, Linux.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
